On the discovery and origin of $r$-process stars in the Milky Way.

### 2018-02-07 article/ms.tex
Name change

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[On the Galactic nucleosynthesis of $r$-process material.]{On the Galactic nucleosynthesis of $r$-process material.}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{metalhistpython}
		\caption{The metallicities of the 47 candidate stars.}
		\label{fig:starindex_423451}
	\end{figure}

@@

	We gathered an initial sample of 62 candidates out of the 454180 LAMOST giant sample. These were then visually scrutinised to identify those that lacked visual evidence that they were enhanced. After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very strong candidates.

@@

	\subsection{Selection effects}
	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$), and don't cluster towards any position in the observed sky. These characteristics argue that the abundance we see could not have originated from a common era or site.

@@

			-               	& {[}deg{]}   & {[}deg{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[On the discovery and origin of r-process stars in the Milky Way.]{On the discovery and origin of $r$-process stars in the Milky Way.}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{metalhistpython}
		\caption{The metallicities of the 47 candidate stars.}
		\label{fig:metallicity}
	\end{figure}

@@

	We gathered an initial sample of 62 candidates out of the 454180 LAMOST giant sample. These were then visually scrutinised to identify those that lacked visual evidence that they were enhanced. After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very strong candidates. An example of one of our candidates is shown in Figure \ref{fig:starindex_423451}.

@@

	\subsection{Selection effects}
	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$) as seen in Figure \ref{fig:metallicity}, and don't cluster towards any position in the observed sky. These characteristics argue that the abundance we see could not have originated from a common era or site.

@@

			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$\rm{cm\ s}^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
